Manuscript Figures for Genome Biology

### 2018-05-28 manuscript_figures/manuscript_figures.Rmd
Remove all Baxter(CRC) studies from Microbiome results figs

# remove microbiome objects from 'null' comparisons
# removing baxter, goodrich and papa OTU-level (since they mostly found 
# nothing for all methods and the genus-level analysis is also present)
null <- which(grepl(c("baxter|goodrich|papa"), objects) & 
              grepl(c("otu"), objects))

@@

Fig4.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                            tableOnly = TRUE)$method)
Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha)
Fig4
ggsave(file.path(outdir, "Figure4a.pdf"), width=6, height=4)

Fig4All.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = alpha, 
                               tableOnly = TRUE, excludeMethods = NULL)$method)
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL)
Fig4All
ggsave(file.path(outdir, "Figure4a_all.pdf"), width=6, height=4)

@@

```{r}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("baxter|goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", Nlabel = FALSE) + 
  ggtitle("Microbiome")
ggsave(file.path(outdir, "FigureS6.pdf"), width=7.5, height=4)
```

>>>>

# remove microbiome objects from 'null' comparisons
# removing baxter, goodrich and papa OTU-level (since they mostly found 
# nothing for all methods and the genus-level analysis is also present)
null <- which(grepl(c("goodrich|papa"), objects) & 
              grepl(c("otu"), objects) | 
              grepl("baxter", objects))

@@

Fig4.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                            tableOnly = TRUE)$method)
Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha)
Fig4

# not excluding any methods
Fig4All.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = alpha, 
                               tableOnly = TRUE, excludeMethods = NULL)$method)
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL)
Fig4All

@@

```{r}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset) &
              !grepl("baxter", dataset) )
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", Nlabel = FALSE) + 
  ggtitle("Microbiome")
ggsave(file.path(outdir, "FigureS6.pdf"), width=7.5, height=4)
```
